### 2015-01-19 src/methodology.Rnw
update

\subsubsection{Constrained Mutation}
\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.} They selected ROR
and ABS from Mothra for mutation analysis. We used operators \Pitcb and
\Pitnc to model ROR operator. There are no comparable operators to ABS in PIT.

@@

\subsubsection{N-selection}
\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested removal of
$n$ most numerous operators. In our experiment, the order of operators was
\Pitnvmc, \Pitrv, \Pitic, \Pitdc, \Pitnc, \Pitrc, \Pitvmc, \Pitcc, \Pitemv,
\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin.
We discarded one at each
step and evaluated the effectiveness at each $n$.
%----------------------------------------
\subsubsection{Statement deletion emulation} \label{subsec:stmtdel}

>>>>

\subsubsection{Constrained Mutation}
\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.} They selected ROR
and ABS from Mothra for mutation analysis. The ABS operator was chosen with
the reasoning that it forces users to consider all parts of the input domain,
and ROR was chosen because it forces users to consider values of predicates.
ROR mutates relational operators, while ABS replaces variables and expressions
by their positive or negative absolute value or zero. \Pitcb and \Pitnc from
PIT are a good map for ROR. However, we could not map ABS to PIT operators.

% ROR Relational Operator Replacement a > b to b < a
% ABS Absolute value insertion a = b to a = abs(b), -abs(b), 0

@@

\subsubsection{N-selection}
\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested
removal of $n$ most numerous operators. In our experiment, the order of
operators was \Pitnvmc, \Pitrv, \Pitic, \Pitdc, \Pitnc, \Pitrc, \Pitvmc,
\Pitcc, \Pitemv, \Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin.
We discarded one at each step and evaluated the effectiveness at each $n$.

\subsubsection{Statement deletion emulation} \label{subsec:stmtdel}
The original statement deletion was proposed by Acree~\cite{acree1980onmutation}.
